Reanalysis Step 5: Outcome Analysis with Three-Way Interaction

### 2025-09-01 reanalysis-5-outcome_analysis-interaction.qmd
testmode
ix

# ANALYSIS MODE: Use same as imputation/PS
analysis_mode <- "final"  # Should match imputation and PS modes

@@

@@

# Pivot to wide format for better readability with percentages
library(tidyr)
crosstab_wide <- crosstab_df |>
  pivot_wider(names_from = Lapse_Status, 
              values_from = Count,
              values_fill = 0,
              names_prefix = "Lapse_") |>  # Add prefix to avoid numeric column names
  arrange(DR_Severity, Treatment) |>
  mutate(
    Total = Lapse_0 + Lapse_1,
    No_Lapse_Pct = paste0(round(100 * Lapse_0 / Total, 1), "%"),
    Lapsed_Pct = paste0(round(100 * Lapse_1 / Total, 1), "%"),
    Row_Pct = paste0(round(100 * Total / total_n, 1), "%")
  ) |>
  select(DR_Severity, Treatment, 
         No_Lapse = Lapse_0, No_Lapse_Pct,
         Lapsed = Lapse_1, Lapsed_Pct,
         Total, Row_Pct)

>>>>

# ANALYSIS MODE: Use same as imputation/PS
analysis_mode <- "test"  # Should match imputation and PS modes

@@

# Convert numeric lapse status to meaningful labels
crosstab_df$Lapse_Status <- factor(crosstab_df$Lapse_Status, 
                                   levels = c("0", "1"),
                                   labels = c("No_Lapse", "Lapsed"))

@@

# Pivot to wide format for better readability with percentages
library(tidyr)
crosstab_wide <- crosstab_df |>
  pivot_wider(names_from = Lapse_Status, 
              values_from = Count,
              values_fill = 0) |>
  arrange(DR_Severity, Treatment) |>
  mutate(
    Total = No_Lapse + Lapsed,
    No_Lapse_Pct = paste0(round(100 * No_Lapse / Total, 1), "%"),
    Lapsed_Pct = paste0(round(100 * Lapsed / Total, 1), "%"),
    Row_Pct = paste0(round(100 * Total / total_n, 1), "%")
  ) |>
  select(DR_Severity, Treatment, 
         No_Lapse, No_Lapse_Pct,
         Lapsed, Lapsed_Pct,
         Total, Row_Pct)
